Analysis

### 2022-01-04 code/R/Analysis.Rmd
Outputs for presentation

```{r}
thul01 = read.csv("../../data/annotations/2020_05_15_NorwayAnnotations_THUL-01_IndividualAnnotations_FRCNN.csv", header = F)

@@

@@

```{r}
d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_NYAA-04_Evaluate.csv")

@@

```
```{r}
# NYAA-04 gt:
nyaa04_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2021_12_13_NorwayAnnotations_NYAA-04_IndividualAnnotations_FRCNN_Metrics.csv")

@@

minmm = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NYAA-04_3/parameterTest_NYAA-04_maxDisap_10_runMean_60_maxDist_300.csv")

@@

@@

```{r}
d2 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_THUL-01_Evaluate.csv")

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllCombinations.png', THUL01_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllZero.png', THUL01_p2)
```
```{r}
# NYAA-04 gt:
thul01_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_15_NorwayAnnotations_THUL-01_IndividualAnnotations_FRCNN_Metrics.csv")

@@

@@

```{r}
d3 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_NARS-04_Evaluate.csv")

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-04_AllCombinations.png', NARS04_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-04_TenLowest.png', NARS04_p2)
```
```{r}
# NYAA-04 gt:
NARS04_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_17_NorwayAnnotations_NARS-04_IndividualAnnotations_FRCNN_Metrics.csv")

@@

minmm = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NARS-04_3/parameterTest_NARS-04_maxDisap_10_runMean_10_maxDist_500.csv")

@@

@@

```{r}
# NYAA-04 gt:
NARS13_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_04_30_NorwayAnnotations_NARS-13_IndividualAnnotations_FRCNN_Metrics.csv")

@@

minmm = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NARS-13_3/parameterTest_NARS-13_maxDisap_0_runMean_0_maxDist_0.csv")

@@

>>>>

```{r}
thul01 = read.csv("../../data/annotations/2020_05_15_NorwayAnnotations_THUL-01_IndividualAnnotations_FRCNN_Metrics.csv", header = T)

@@

nars04$x_c = (nars04$x_min + nars04$x_max) / 2
nars04$y_c = (nars04$y_min + nars04$y_max) / 2

@@

```{r fig.height=4}
d1 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_NYAA-04_Evaluate.csv")

@@

```{r}
# NYAA-04 gt:
nyaa04_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2021_12_13_NorwayAnnotations_NYAA-04_IndividualAnnotations_FRCNN_Metrics.csv")

@@

nyaa04minmm = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NYAA-04_3/parameterTest_NYAA-04_maxDisap_10_runMean_60_maxDist_300.csv")

@@

```{r fig.height=4}

nyaa04minmm %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(objectID)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NYAA-04 Tracked (Minimum mm)") +
  theme(legend.position = "none")

nyaa04 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(Class)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NYAA-04 Ground Truth") +
  theme(legend.position = "none")
```

@@

```{r fig.height=4}
d2 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_THUL-01_Evaluate.csv")

@@

ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllCombinations.png', THUL01_p1)
ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/THUL-01_AllZero.png', THUL01_p2)
```

```{r}
# NYAA-04 gt:
thul01_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_15_NorwayAnnotations_THUL-01_IndividualAnnotations_FRCNN_Metrics.csv")

@@

```{r fig.height=4}

cornoo %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(objectID)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("THUL-01 Tracked") +
  theme(legend.position = "none")

thul01 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(id_gt)), size = 1, shape = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("THUL-01 Ground Truth") +
  theme(legend.position = "none")
```

@@

```{r fig.height=4}

d3 = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/parameterTest_3_NARS-04_Evaluate.csv")

@@

NARS04_p1
NARS04_p2

#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-04_AllCombinations.png', NARS04_p1)
#ggsave('U:/BITCue/Projekter/TrackingFlowers/testResults/figures/NARS-04_TenLowest.png', NARS04_p2)
```

```{r}
# NARS-04 gt:
NARS04_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_05_17_NorwayAnnotations_NARS-04_IndividualAnnotations_FRCNN_Metrics.csv")

@@

nars04minmm = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NARS-04_3/parameterTest_NARS-04_maxDisap_10_runMean_10_maxDist_500.csv")

@@

```{r fig.height=4}

nars04minmm %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(objectID)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NARS-04 Tracked") +
  theme(legend.position = "none")

nars04 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(Class)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NARS-04 Ground Truth") +
  theme(legend.position = "none")
```

@@

```{r}
# NARS-13 gt:
NARS13_gt = read.csv("U:/BITCue/Projekter/TrackingFlowers/data/annotations/2020_04_30_NorwayAnnotations_NARS-13_IndividualAnnotations_FRCNN_Metrics.csv")

@@

```{r}
# Minimum mm: 10-20, 300-400, 10, 78, 0.9840393, 81+85+93+97
# All zero: 0, 0, 0, 267, 0.9453653, 88
# Correct noo with minimum mm: 10, 400, 10, 78, 0.9840393, 85

nars13minmm = read.csv("U:/BITCue/Projekter/TrackingFlowers/testResults/_parameterTest_NARS-13_3/parameterTest_NARS-13_maxDisap_0_runMean_0_maxDist_0.csv")

@@

```{r fig.height=4}

nars13minmm %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(objectID)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NARS-13 Tracked (Minimum mm)") +
  theme(legend.position = "none")

nars13 %>% 
  ggplot() +
  geom_point(aes(x = x_c, y = y_c, color = as.factor(Class)), size = 1) + 
  xlim(0,6080) +
  ylim(0,3420) + 
  ggtitle("NARS-13 Ground Truth") +
  theme(legend.position = "none")

length(unique(nars13$Class))
```
